A Horrocks-type theorem for even orthogonal $K_2$

### 2019-11-24 dl-paper.tex
Update grant line

\subsection{Acknowledgements} 
The authors of this paper were also supported by ``Native towns'', a social investment program of PJSC ``Gazprom Neft''.
The second-named author also acknowledges the financial support of RFBR grant No 18-31-20044.

>>>>

\subsection{Acknowledgements} 
The first-named author acknowledges the financial support of Russian Science Foundation grant No 17-11-01261.
The second-named author acknowledges the financial support of RFBR grant No 18-31-20044.
